---
title: "Bootstrapping explanation"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(mixRSVP)
library(reshape2)
```

#Boostrapping Procedure Explainer
The motivation for this procedure is to find an analysis that tests for the presence of non-guesses from before the cue without relying on the mixture modelling. 

To start with, we generate a distribution of guesses. First we pull the data for one participant in one condition.

```{r}
allErrors <- read.csv('../allErrors18Streams.txt', header = T, stringsAsFactors = F) #All our RSVP data for the 18streams experiment

theseData <- allErrors %>% filter(ID == '18JG', condition == 2)
```

The distribution of responses for this participant looks like this.

```{r}
ggplot(allErrors, aes(x = SPE))+
  geom_histogram(binwidth = 1)+
  labs(y = 'Count', x = 'SPE')+
  facet_wrap(~ID+condition)

empiricalHist <- ggplot(theseData, aes(x = SPE))+
  geom_histogram(binwidth = 1, aes(fill = SPE == -1))+
  scale_fill_manual(values = c('TRUE' = '#ffa951', 'FALSE' = '#628093'), guide = FALSE)+
  labs(y = 'Count', x = 'SPE')+
  theme_apa()
```

Now that we have this data, we can create a distribution of guesses. This assumes that all the responses were guesses, which is obviously untrue. 

```{r}
nTrials <- nrow(theseData)
numItemsInStream = 24

#############################
###Generate pseudo-uniform###
#############################

maxSPETheseData <- theseData %>% pull(targetSP) %>% max
minSPETheseData <- theseData %>% pull(targetSP) %>% min
minSPE <- 1 - maxSPETheseData
maxSPE <- numItemsInStream - minSPETheseData

guessingDist <- createGuessingDistribution(minSPE = minSPE,
                                           maxSPE = maxSPE,
                                           targetSP = theseData$targetSP,
                                           numItemsInStream = numItemsInStream)

guessingDist <- guessingDist/sum(guessingDist)

pseudoUniform <- data.frame(
  xDomain = minSPE:maxSPE, 
  guessingDist = guessingDist, 
  prob = guessingDist/sum(guessingDist)) #Prob is the probabilty of a particular response
```

The distribution we'd expect if all responses were guesses would look like this.

```{r echo = F}
pseudoUnifHist <- ggplot(pseudoUniform, aes(x = xDomain, y = guessingDist))+
  geom_bar(width = 1, stat = 'identity', aes(fill = xDomain == -1))+
  scale_fill_manual(values = c('TRUE' = '#ffa951', 'FALSE' = '#628093'), guide = FALSE)+
  labs(y = 'Count', x = 'SPE')+
  scale_x_continuous(breaks = seq(minSPE,maxSPE,2))+
  theme_apa()
```

But this is wrong! We want to scale it down a bit so that 

```{r}

runAnyway <- FALSE

bootstrapPValue <- function(theseData, numItemsInStream, whichSPE, nReps){
  nTrials <- nrow(theseData)

  #############################
  ###Generate pseudo-uniform###
  #############################
  
  thisAccuracy <- length(which(theseData$SPE == 0))/nTrials
  
  thisGuessingRate <- 1 - thisAccuracy
  print(thisAccuracy)
  print(thisGuessingRate)
  
  maxSPETheseData <- theseData %>% pull(targetSP) %>% max
  minSPETheseData <- theseData %>% pull(targetSP) %>% min
  minSPE <- 1 - maxSPETheseData
  maxSPE <- numItemsInStream - minSPETheseData

  guessingDist <- createGuessingDistribution(minSPE = minSPE,
                                             maxSPE = maxSPE,
                                             targetSP = theseData$targetSP,
                                             numItemsInStream = numItemsInStream)

  pseudoUniform <- data.frame(xDomain = minSPE:maxSPE, guessingDist = guessingDist, prob = guessingDist/sum(guessingDist)) #give guessing dist values labels

  

  nWhichSPE <- theseData %>% filter(SPE == whichSPE) %>% nrow() #How many observations at SPE = whichSPE?

  bootstraps <- data.frame(rep = 1:nReps, #store the counts of whichSPE sampled from the pseudouniform here.
                           count = -999)

  for(i in 1:nReps){
    thisSample <- sample(pseudoUniform$xDomain, prob = pseudoUniform$prob, replace = T, size = nTrials*thisGuessingRate) #sample nTrials many trials from the pseudouniform over the range of possible SPEs in this experiment
    nThisSPE<- which(thisSample == whichSPE) %>% length #How many of the trials had an SPE == whichSPE
    bootstraps %<>% mutate(count = replace(count, rep == i, nThisSPE)) #Put the count nThisSPE in the dataframe
  }

  return(length(which(bootstraps$count>=nWhichSPE))/nReps) #a p.value. The proportion of bootstrapped samples that had a count of whichSPE at least as great as the observed count

}


numItemsInStream = 24

pFiles <- list.files(pattern = 'bootstrapPValues18Streams.*.csv',
                     path = '..',
                     full.names = T)



if(length(pFiles)>0 & !runAnyway){
  splits <- pFiles %>% strsplit(x = .,
                                split = '18Streams|\\.csv')
  
  
  dates <- lapply(splits,
                  FUN = function(x){
                    x[2] %>% as.POSIXct(., format = "%d-%m-%Y_%H-%M-%S")
                  }) %>% unlist
  
  whichLatestDate <- which(dates == max(dates))
  
  ps <- read.csv(pFiles[whichLatestDate])
} else{
  ps <- expand.grid(xDomain = -9:9,
                    p = -1,
                    participant = unique(allErrors$ID),
                    condition = unique(allErrors$condition))
  for(thisParticipant in unique(allErrors$ID)[1:3]){
    print(thisParticipant)
    for(thisCondition in unique(allErrors$condition)){
      print(thisCondition)
      theseData <- allErrors %>% filter(ID == thisParticipant & condition == thisCondition)
      for(whichSPE in c(-1)){
        print(whichSPE)
        thisP <- bootstrapPValue(theseData,numItemsInStream,whichSPE,10000)
        ps %<>% mutate(p = replace(p, xDomain == whichSPE & participant == thisParticipant & condition == thisCondition, thisP))
      }
    }
  }
  #write.csv(ps, paste0('Analysis/bootstrapPValues18Streams',format(Sys.time(), "%d-%m-%Y_%H-%M-%S"),'.csv'),row.names = F)
}

ps %<>% filter(participant != '18TR1')

ps %>% filter(p != -1) %>% ggplot(., aes(x = xDomain, y = p))+
  geom_line(aes(colour = factor(condition)))+
  facet_wrap(~participant,nrow = 3)+
  geom_hline(yintercept = .05, linetype = 'dashed')+
  geom_vline(xintercept = -1, linetype = 'dashed')+
  labs(x = 'SPE', y = 'p', colour = 'nStream')

table <- ps %>% group_by(condition, xDomain) %>% summarise(nSig = length(which(p<.05)))

table %<>% mutate(milliseconds = xDomain*(1000/12))

table %>% dcast(.,
                xDomain ~ condition,
                value.var = 'nSig')

bootstrapPlot <- table %>% ggplot(., aes(x=xDomain, y = nSig))+
  geom_line(aes(linetype = factor(condition)),size = 1)+
  scale_x_continuous(breaks = -9:9)+
  scale_y_continuous(breaks = seq(0,12,3))+
  labs(x = 'SPE', y = 'Deviations from Guessing',linetype = 'nStreams')

ggsave(filename = '../../modelOutput/18Streams/bootstrapPlot.png',
       plot = bootstrapPlot,
       height=15, 
       width=20,
       units='cm')


```

```{r}
###Plot some samples for the explanation plot###

  nTrials <- nrow(theseData)

  #############################
  ###Generate pseudo-uniform###
  #############################
  
  thisAccuracy <- length(which(theseData$SPE == 0))/nTrials
  
  thisGuessingRate <- 1 - thisAccuracy
  print(thisAccuracy)
  print(thisGuessingRate)
  
  maxSPETheseData <- theseData %>% pull(targetSP) %>% max
  minSPETheseData <- theseData %>% pull(targetSP) %>% min
  minSPE <- 1 - maxSPETheseData
  maxSPE <- numItemsInStream - minSPETheseData

  guessingDist <- createGuessingDistribution(minSPE = minSPE,
                                             maxSPE = maxSPE,
                                             targetSP = theseData$targetSP,
                                             numItemsInStream = numItemsInStream)

  pseudoUniform <- data.frame(xDomain = minSPE:maxSPE, guessingDist = guessingDist, prob = guessingDist/sum(guessingDist)) #give guessing dist values labels

  

  nWhichSPE <- theseData %>% filter(SPE == -1) %>% nrow() #How many observations at SPE = whichSPE?

  bootstraps <- expand.grid(rep = 1:12, #store the counts of whichSPE sampled from the pseudouniform here.
                           SPE = rep(-999, times = nTrials*thisGuessingRate))

  for(i in 1:12){
    thisSample <- sample(pseudoUniform$xDomain, prob = pseudoUniform$prob, replace = T, size = nTrials*thisGuessingRate) #sample nTrials many trials from the pseudouniform over the range of possible SPEs in this experiment
    bootstraps[bootstraps$rep == i,'SPE'] = thisSample
    
  }

  facetLabels = function(x){ #Dummy function for empty facet labels
    return('')
  }
  
  samplePlot <- ggplot(bootstraps, aes(x = SPE))+
    geom_histogram(binwidth = 1, aes(fill = SPE == -1))+
    scale_fill_manual(values = c('TRUE' = '#ffa951', 'FALSE' = '#628093'), guide = F)+
    labs(y = 'Count', x = 'SPE')+
    facet_wrap(~rep,ncol = 3, labeller = facetLabels)+
    theme_apa()
    
  samplePlot
  ##Show the distribution of counts###
  
  bootstraps <- data.frame(rep = 1:5000, #store the counts of whichSPE sampled from the pseudouniform here.
                           count = -999)

  for(i in 1:5000){
    thisSample <- sample(pseudoUniform$xDomain, prob = pseudoUniform$prob, replace = T, size = nTrials*thisGuessingRate) #sample nTrials many trials from the pseudouniform over the range of possible SPEs in this experiment
    nThisSPE<- which(thisSample == -1) %>% length #How many of the trials had an SPE == whichSPE
    bootstraps %<>% mutate(count = replace(count, rep == i, nThisSPE)) #Put the count nThisSPE in the dataframe
  }
  
  bootFreqPlot <- ggplot(bootstraps, aes(x = count))+
    geom_histogram(binwidth = 1, aes(fill = count >= nWhichSPE))+
    scale_fill_manual(values = c('TRUE' = '#ffa951', 'FALSE' = '#628093'), guide = F)+
    labs(y = 'Frequency', x = 'Count of SPE = -1')+
    theme_apa()
  


ggsave(plot = bootFreqPlot, filename = '../../manuscripts_etc/Manuscript Figures/Bootstrap Explainer/bootFrequencies.png', height = 5, width = 5, units = 'in')
ggsave(plot = samplePlot, filename = '../../manuscripts_etc/Manuscript Figures/Bootstrap Explainer/someSamples.png', height = 5, width = 5, units = 'in')
ggsave(plot = pseudoUnifHist, filename = '../../manuscripts_etc/Manuscript Figures/Bootstrap Explainer/pseudoUnifrom.png', height = 5, width = 5, units = 'in')
ggsave(plot = empiricalHist, filename = '../../manuscripts_etc/Manuscript Figures/Bootstrap Explainer/empiricalHistogram.png', height = 5, width = 5, units = 'in')
```