---
title: "nStreams Analysis: Precue Experiment"
author: "Charlie Ludowici"
date: "5/18/2017"
output: github_document
---

```{r}
library(ggplot2)
library(reshape2)
library(papaja)
theme_set(theme_apa(base_size = 15) ) 

savePlots <- F
nParticipants = 13

horizErrorBars <- function(data, var.name){
  SPEs <- data[,var.name]
  otherColumn <- colnames(data)[which(colnames(data)!=var.name & colnames(data) != 'participant' & colnames(data) != 'Parameter')]
  y = mean(data[,otherColumn], na.rm=T)
  se = sqrt(var(SPEs)/length(which(!is.na(SPEs))))
  xmin <- mean(SPEs, na.rm=T) - se
  xmax <- mean(SPEs, na.rm=T) + se
  x = mean(SPEs, na.rm=T)
  data.frame(x=x, xmin=xmin, xmax=xmax, y=y)
}

vertErrorBars <- function(data, var.name){
  SPEs <- data[,var.name]
  otherColumn <- colnames(data)[which(colnames(data)!=var.name & colnames(data) != 'participant' & colnames(data) != 'Parameter')]
  x = mean(data[,otherColumn], na.rm=T)
  se = sqrt(var(SPEs)/length(which(!is.na(SPEs))))
  ymin <- mean(SPEs, na.rm=T) - se
  ymax <- mean(SPEs, na.rm=T) + se
  y = mean(SPEs, na.rm=T)
  data.frame(x=x, ymin=ymin, ymax=ymax, y=y)
}


posterior <- function(t, N1, N2=NULL, delta, lo=-Inf, hi = Inf,
                      priorMean=0,priorSD=1) {
        N = ifelse(is.null(N2), N1, N1*N2/(N1+N2))
        df  = ifelse(is.null(N2), N1 - 1, N1 + N2 - 2)
        
        #prior and likelihood
        #prior <- function(delta) dnorm(delta, priorMean, priorSD)*as.integer(delta >= lo)*as.integer(delta <= hi) 
        prior <- function(delta) dcauchy(delta, priorMean, priorSD)*as.integer(delta >= lo)*as.integer(delta <= hi) 
        K=1/integrate(prior,lower=lo,upper=hi)[[1]]
        f=function(delta) K*prior(delta)
        
        #(The as.integer bits above just provide bounds for the prior if you want them)
      
        likelihood <- function(delta) dt(t, df, delta*sqrt(N))
        
        #marginal likelihood
        marginal <- integrate(function(x) f(x)*likelihood(x), lo, hi)[[1]]
        
        #posterior
        post <- function(x) f(x)*likelihood(x) / marginal
        return(post(delta))
}


```

```{r message=FALSE}

null = 0

MMlatency <- read.csv('../modelOutput/precueCSV/TGRSVP_Exp2_LatencyNorm.csv')
MMprecision <- read.csv('../modelOutput/precueCSV/TGRSVP_Exp2_precisionNorm.csv')
MMefficacy <- read.csv('../modelOutput/precueCSV/TGRSVP_Exp2_efficacyNorm.csv')

latency <- data.frame(twoStreams = MMlatency$SingleLeft[MMlatency$Group == 1], eightStreams = MMlatency$SingleLeft[MMlatency$Group == 2])
latency <- latency[complete.cases(latency),]
latency$participant <- factor(1:nParticipants)

precision <- data.frame(twoStreams = MMprecision$SingleLeft[MMprecision$Group == 1], eightStreams = MMprecision$SingleLeft[MMprecision$Group == 2])
precision <- precision[complete.cases(precision),]
precision$participant <- factor(1:nParticipants)

efficacy <- data.frame(twoStreams = MMefficacy$SingleLeft[MMefficacy$Group == 1], eightStreams = MMefficacy$SingleLeft[MMefficacy$Group == 2])
efficacy <- efficacy[complete.cases(efficacy),]
efficacy$participant <- factor(1:nParticipants)

frequentistTestLatency = t.test(x = latency$eightStreams, y=latency$twoStreams, paired = T)
tLatency <- frequentistTestLatency$statistic[[1]]
frequentistTestLatency
```
#Method

Participants viewed a screen from a distance of 59cm in a dark, soundproof room. Participants performed 240 trials in one block. On each trial, the program presented participants with a fixation point and 8 simultaneous RSVP streams of 3 degree high Sloan letters. Each stream was the alphabet in a random order. Letters were presented at a rate of 12/second. At one point and in one stream on each trial, a letter appeared with a white circle around it. Participants' task was to report this letter. Participants saw a series of hashmarks at the same position as the RSVP streams before the presentation of the streams. The potential positions of the cued stream were indicated with white circles around the hash marks in this array. The number of pre-cued streams was either two or eight. The position of the pre-cued streams in the two streams condition reproduced those of the streams in the original nStreams experiment's two streams condition. The hashmarks and pre-cues were on screan for 150
#Latency Analyses

```{r warning=FALSE}
latencyForPlot <- melt(latency, measure.vars = c('twoStreams','eightStreams'),variable.name = 'Condition', value.name = 'Estimate')
latencyForPlot$Participant <- ordered(rep(1:nParticipants, times = 2))

t  <- tLatency
N1 <- nParticipants
N2 <- nParticipants

priorMean = null
priorSD = sqrt(.5)

#examples of BF via savage-dickey ratio
#2-sided
BF10 = dcauchy(null,priorMean,priorSD) / posterior(tLatency, N1, delta=null,
                                              priorMean=priorMean,priorSD=priorSD)

#one-sided BF
BFplus = ( 2 * dcauchy(null,priorMean,priorSD) ) / posterior(tLatency, N1, delta=null, lo=0,
                                            priorMean=priorMean,priorSD=priorSD)

BF10
BFplus

delta  <- seq(-2, 4, .01)

posteriorAndPriorDF <- data.frame(delta = delta, posterior = posterior(t,N1,delta=delta, priorMean=priorMean,priorSD=priorSD), prior = dcauchy(delta, priorMean,priorSD))

posteriorModeLatency <- optimize(function(delta) posterior(tLatency, N1, delta=delta, priorMean=priorMean, priorSD=priorSD), interval=c(-4,4),maximum = T)[[1]]

#This would only work for normal, we use Cauchy!
#credibleIntervalDensityLower <- mean(posteriorAndPriorDF$posterior)-sd(posteriorAndPriorDF$posterior)*1.96
#credibleIntervalDensityUpper <- mean(posteriorAndPriorDF$posterior)+sd(posteriorAndPriorDF$posterior)*1.96


latencyPlot <- ggplot(latencyForPlot,aes(x=Condition, y=Estimate))+
  geom_violin()+
  geom_line(aes(group=Participant, colour=Participant))+
  geom_point(aes(colour=Participant), size = 3)+
  scale_colour_brewer(palette = 'Spectral')+
  labs(x='Condition',y='Estimate (ms)',title='Latency')+
  theme(plot.title = element_text(hjust=.5))

show(latencyPlot)

latencyHorizSE <- horizErrorBars(latency, 'twoStreams')
latencyVertSE <- vertErrorBars(latency, 'eightStreams')

latencyScatter <- ggplot(latency, aes(x=twoStreams, y=eightStreams))+
  geom_point(size = 4, aes(colour=participant))+
  scale_color_brewer(palette='Spectral', name='Participant')+
  geom_point(data = data.frame(x=mean(latency$twoStreams, na.rm=T), y = mean(latency$eightStreams, na.rm=T)), aes(x=x,y=y, shape = 'Mean'), size = 10, inherit.aes = F)+
  geom_errorbarh(data = latencyHorizSE, aes(x=x, xmin=xmin, xmax = xmax, y=y),inherit.aes = F, height=10)+
  geom_errorbar(data=latencyVertSE, aes(x=x, ymin=ymin,ymax=ymax, y=y), inherit.aes = F, width = 10)+
  scale_shape_manual(values=c('Mean' = 9), labels = NULL, name = "Mean")+
  lims(x=c(20,300), y=c(20,300))+
  labs(title='Latency Estimates (ms)', x = 'Two Streams', y='Eight Streams')+
  theme(plot.title = element_text(size=15, hjust=.5))+
  annotate('text', x=100, y=45, label = paste0('BF10 = ', round(BF10,2)))+
  annotate('text', x = 100, y=37, label = paste0('Effect size = ', round(posteriorModeLatency,2)))+
  geom_abline(intercept = 0, slope = 1,linetype='dashed')+
  coord_fixed()

show(latencyScatter)



latencyBayesPlot <- ggplot(posteriorAndPriorDF, aes(x=delta))+
  geom_line(aes(y=posterior, linetype = 'Posterior'))+
  geom_line(aes(y=prior, linetype = 'Prior'))+
  scale_linetype_manual(values = c('solid','dashed'),  guide = 'legend', name = NULL)+
  labs(x = expression(delta), y='Density', title = 'Latency Effect Size')

show(latencyBayesPlot)
```

#Precision Analysis

```{r warning=FALSE}
precisionForPlot <- melt(precision, measure.vars = c('twoStreams','eightStreams'),variable.name = 'Condition', value.name = 'Estimate')
precisionForPlot$Participant <- ordered(rep(1:nParticipants, times = 2))


frequentistTestPrecision <- t.test(x = precision$eightStreams, y = precision$twoStreams, paired = T)
tPrecision <- frequentistTestPrecision$statistic[[1]]

t  <- tPrecision
N1 <- nParticipants
N2 <- nParticipants

priorMean =0
priorSD = sqrt(.5)

#examples of BF via savage-dickey ratio
#2-sided
BF10 = dcauchy(0,priorMean,priorSD) / posterior(tPrecision, N1, delta=0,
                                              priorMean=priorMean,priorSD=priorSD)

#one-sided BF
BFplus = ( 2 * dcauchy(0,priorMean,priorSD) ) / posterior(tPrecision, N1, delta=0, lo=0,
                                            priorMean=priorMean,priorSD=priorSD)

BF10
BFplus

delta  <- seq(-4, 2, .01)

posteriorModePrecision <- optimize(function(delta) posterior(tPrecision, N1, delta=delta,priorMean=priorMean,priorSD=priorSD), interval=c(-4,4),maximum = T)[[1]]

posteriorAndPriorDF <- data.frame(delta = delta, posterior = posterior(t,N1,delta=delta,
                                                                       priorMean=priorMean,priorSD=priorSD), prior = dcauchy(delta, priorMean,priorSD))

posteriorModePrecision <- optimize(function(delta) posterior(tPrecision, N1, delta=delta, priorMean=priorMean, priorSD=priorSD), interval=c(-4,4),maximum = T)[[1]]


precisionPlot <- ggplot(precisionForPlot,aes(x=Condition, y=Estimate))+
  geom_violin()+
  geom_line(aes(group=Participant, colour=Participant))+
  geom_point(aes(colour=Participant),alpha=.8, size = 3)+
  scale_colour_brewer(palette = 'Spectral')+
  labs(x='Condition',y='Estimate (ms)',title='Precision')+
  theme(plot.title = element_text(hjust=.5))

show(precisionPlot)

precisionHorizSE <- horizErrorBars(precision, 'twoStreams')
precisionVertSE <- vertErrorBars(precision, 'eightStreams')


precisionScatter <- ggplot(precision, aes(x=twoStreams, y=eightStreams, colour = participant))+
  geom_point(size = 4)+
  scale_color_brewer(palette='Spectral', name='Participant')+
  geom_point(data = data.frame(x=mean(precision$twoStreams, na.rm=T), y = mean(precision$eightStreams, na.rm=T)), aes(x=x,y=y, shape = 'Mean'), size = 10, inherit.aes = F)+
  geom_errorbarh(data = precisionHorizSE, aes(x=x, xmin=xmin, xmax = xmax, y=y),inherit.aes = F, height=10)+
  geom_errorbar(data=precisionVertSE, aes(x=x, ymin=ymin,ymax=ymax, y=y), inherit.aes = F, width = 10)+
  scale_shape_manual(values=c('Mean' = 9), labels = NULL, name = "Mean")+
  lims(x=c(40,200), y=c(40,200))+
  labs(title='Precision Estimates (ms)')+
  theme(plot.title = element_text(size=15, hjust=.5))+
  annotate('text', x=170, y=70, label = paste0('BF10 = ', round(BF10,2)))+
  annotate('text', x = 170, y=60, label = paste0('Effect size = ', round(posteriorModePrecision,2)))+
  geom_abline(intercept = 0, slope = 1,linetype='dashed')+
  coord_fixed()

show(precisionScatter)

precisionBayesPlot <- ggplot(posteriorAndPriorDF, aes(x=delta))+
  geom_line(aes(y=posterior, linetype = 'Posterior'))+
  geom_line(aes(y=prior, linetype = 'Prior'))+
  scale_linetype_manual(values = c('solid','dashed'),  guide = 'legend', name = NULL)+
  labs(x = expression(delta), y='Density', title = 'Precision Effect Size')

show(precisionBayesPlot)


```

#Efficacy Analysis

```{r warning=FALSE}
frequentistTestEfficacy <- t.test(x = efficacy$eightStreams, y = efficacy$twoStreams, paired = T)
tEfficacy <- frequentistTestEfficacy$statistic[[1]]

efficacyForPlot <- melt(efficacy, measure.vars = c('twoStreams','eightStreams'), variable.name = 'Condition',value.name = 'Estimate')
efficacyForPlot$Participant <- ordered(rep(1:nParticipants, times = 2))

t  <- tEfficacy
N1 <- nParticipants
N2 <- nParticipants

priorMean =0
priorSD = sqrt(.5)

#examples of BF via savage-dickey ratio
#2-sided
BF10 = dcauchy(0,priorMean,priorSD) / posterior(tEfficacy, N1, delta=0,
                                              priorMean=priorMean,priorSD=priorSD)

#one-sided BF
BFplus = ( 2 * dcauchy(0,priorMean,priorSD) ) / posterior(tEfficacy, N1, delta=0, lo=0,
                                            priorMean=priorMean,priorSD=priorSD)

BF10
BFplus

delta  <- seq(-2, 4, .01)

posteriorAndPriorDF <- data.frame(delta = delta, posterior = posterior(t,N1,delta=delta,
                                                                       priorMean=priorMean,priorSD=priorSD), prior = dcauchy(delta, priorMean,priorSD))

posteriorModeEfficacy <- optimize(function(delta) posterior(tEfficacy, N1, delta=delta,priorMean=priorMean,priorSD=priorSD), interval=c(-4,4),maximum = T)[[1]]


efficacyPlot <- ggplot(efficacyForPlot, aes(x=Condition, y=Estimate))+
  geom_violin()+
  geom_line(aes(group=Participant, colour=Participant))+
  geom_point(aes(colour = Participant), size = 3)+
  labs(x='Condition',y='Estimate',title='Efficacy')+
  theme(plot.title = element_text(hjust=.5))+
  scale_colour_brewer(palette = 'Spectral')

show(efficacyPlot)

efficacyHorizSE <- horizErrorBars(efficacy, 'twoStreams')
efficacyVertSE <- vertErrorBars(efficacy, 'eightStreams')

efficacyScatter <- ggplot(efficacy, aes(x=twoStreams, y=eightStreams, colour=participant))+
  geom_point(size = 4)+
  scale_color_brewer(palette='Spectral', name='Participant')+
  geom_point(data = data.frame(x=mean(efficacy$twoStreams, na.rm=T), y = mean(efficacy$eightStreams, na.rm=T)), aes(x=x,y=y, shape = 'Mean'), size = 10, inherit.aes = F)+
  geom_errorbarh(data = efficacyHorizSE, aes(x=x, xmin=xmin, xmax = xmax, y=y),inherit.aes = F, height=.01)+
  geom_errorbar(data=efficacyVertSE, aes(x=x, ymin=ymin,ymax=ymax, y=y), inherit.aes = F, width = .01)+
  scale_shape_manual(values=c('Mean' = 9), labels = NULL, name = "Mean")+
  lims(x=c(0,1), y=c(0,1))+
  labs(title='Efficacy Estimates [1 - P(Guess)]', y = 'Eight Streams', y='Eight Streams')+
  theme(plot.title = element_text(size=15, hjust=.5))+
  annotate('text', x=.8, y=.45, label = paste0('BF10 = ', round(BF10,2)))+
  annotate('text', x = .8, y=.37, label = paste0('Effect size = ', round(posteriorModeEfficacy,2)))+
  geom_abline(intercept = 0, slope = 1,linetype='dashed')+
  coord_fixed()

show(efficacyScatter)

efficacyBayesPlot <- ggplot(posteriorAndPriorDF, aes(x=delta))+
  geom_line(aes(y=posterior, linetype = 'Posterior'))+
  geom_line(aes(y=prior, linetype = 'Prior'))+
  scale_linetype_manual(values = c('solid','dashed'),  guide = 'legend', name = NULL)+
  labs(x = expression(delta), y='Density', title = 'Efficacy Effect Size')

show(efficacyBayesPlot)

```

```{r}

efficacy$Parameter <- as.character('Efficacy')
latency$Parameter <- as.character('Latency')
precision$Parameter <- as.character('Precision')

allParams <- rbind(efficacy,latency,precision)

allParams <- melt(allParams, measure.vars = c('twoStreams','eightStreams'), variable.name = 'Condition',value.name = 'Estimate')

paramBar <- ggplot(allParams[!allParams$Parameter=='Efficacy',], aes(x=Parameter,y=Estimate, fill = Condition))+
  stat_summary(geom='bar', fun.y = mean, position = position_dodge(.9))+
  stat_summary(geom='errorbar', fun.data=mean_se, position = position_dodge(.9), width = .3)+
  scale_fill_brewer(palette = 'Spectral')

paramBar

predictions <- data.frame(twoStreams = rnorm(1000, latency$twoStreams[7], precision$twoStreams[7]), eightStreams = rnorm(1000, latency$eightStreams[7], precision$eightStreams[7]))

predictions <- melt(predictions, measure.vars = c('twoStreams', 'eightStreams'), variable.name = 'Condition', value.name = 'response')

meanLatencyTwo <- mean(latency$twoStreams)
meanLatencyEight <- mean(latency$eightStreams)

meanPrecisionTwo <- mean(precision$twoStreams)
meanPrecisionEight <- mean(precision$eightStreams)


predictionPlot <- ggplot()+
  stat_function(data=data.frame(x=c(-400:400)/83.33), aes(x, fill = 'Two Streams'), fun = dnorm, args = list(mean = meanLatencyTwo/83.33, sd = meanPrecisionTwo/83.33), geom='area', alpha = .5)+
  stat_function(data=data.frame(x=c(-400:400)/83.33), aes(x, fill = 'Eight Streams'), fun = dnorm, args = list(mean = meanLatencyEight/83.33, sd = meanPrecisionEight/83.33), geom='area', alpha = .6)+
  scale_fill_brewer(palette = 'Set1')+
  scale_x_continuous(breaks = -3:4,limits = c(-3,4))+
  labs(x='SPE', y=NULL, fill = 'Condition')

predictionPlot


if(savePlots){
  ggsave(precisionPlot, file = 'precisionViolin.png', height=15, width=20,units='cm')
  ggsave(latencyPlot, file = 'latencyViolin.png', height=15, width=20,units='cm')
  ggsave(efficacyPlot, file = 'efficacyViolin.png', height=15, width=20,units='cm')
  
  ggsave(precisionScatter, file = 'precisionScatter.png', height=15, width=20,units='cm')
  ggsave(latencyScatter, file = 'latencyScatter.png', height=15, width=20,units='cm')
  ggsave(efficacyScatter, file = 'efficacyScatter.png', height=15, width=20,units='cm')
  
  
  ggsave(efficacyBayesPlot, file = 'efficacyEffectSize.png', height=15, width=20,units='cm')
  ggsave(latencyBayesPlot, file = 'latencyEffectSize.png', height=15, width=20,units='cm')
    ggsave(precisionBayesPlot, file = 'precisionEffectSize.png', height=15, width=20,units='cm')
}
```